Placeholder

### 2021-02-18 Paper_Histograms.Rmd
Recoded 'Mixed or multiple ethinic origins' to be shorter for the final merged retro plot

>>>>

```{r Recode ethnicity levels and re-create non-white plot}

levels(dat.retro_ethnicity_non_white$Ethnicity_collapsed)

dat.retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
                       "Mixed or multiple origins" = "Mixed or multiple ethnic origins"))

arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  #theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))
